---
title: "Getting started with AusCovid19"
author: "Dilinie Seimon"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with AusCovid19}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Background

In December 2019, cases of severe respiratory illness began to be reported across the city of Wuhan in China. Caused by a new type of coronavirus, the disease is now commonly referred to as COVID-19 and was first confirmed in Australia in late January 2020. Since then, COVID-19 has spread across all states of Australia and caused many deaths.

The aim of the AusCovid19 package is to visualise the spread of COVID-19 in Australia and compare the spread across states.
The application visualizes the number of confirmed COVID-19 cases, recoveries and deaths reported due to COVID-19 in Australia at date, as well as the trend of spread across the states over time. Further, the dashboard also provides the daily case numbers reported in each state.

## Installation

The development version of the AusCovid19 package can be installed from [GitHub](https://github.com/etc5523-2020/r-package-assessment-dilinie-seimon) with:

```{r eval=FALSE}
# install.packages("remotes")
remotes::install_github("etc5523-2020/r-package-assessment-dilinie-seimon")
```

## Usage

The `download data()` function allows retreival of state level COVID-19 cases (confirmed, recoveries and deaths) in Australia, and can be either 'cumulative' or 'daily' case counts.

```{r setup, echo=FALSE}
library(AusCovid19)
```

```{r eval=FALSE}
#downloading cumulative COVID-19 data
cum_df <- download_data("cumulative")

#downloading daily COVID-19 data
daily_df <- download_data("daily")
```

The `calculate_daily_counts()` function takes the cumulative counts dataframe as an input and returns the respective daily counts dataframe.

```{r eval=FALSE}
calculate_daily_counts(cum_df)
```

The `get_case_count()` function returns the case count of a given type of cases (either confirmed, recoveries or deaths at a given date)

```{r eval=FALSE}
#get cumulative confirmed case count on 2020-06-05
get_case_count(cum_df, "2020-06-05", "Confirmed")

#get daily death count on 2020-06-05
get_case_count(daily_df, "2020-06-05", "Deaths")
```

The `generate_value_box()` function takes a numeric vector, text label, icon and color as input arguments and returns an html value-box widget of the specified color with the sum of the vector as the value, text label as the subtitle and the icon.

```{r eval=FALSE}
generate_value_box(get_case_count(daily_df, "2020-06-05", "Confirmed"), text="Confirmed Cases", icon="head-side-mask", color="aqua")
```

The `launch_app()` function launches a Shiny application visualizing the spread of COVID-19 across the states of Australia.